\chapter{Nonfunctional Requirements}
\label{chapt-nonfunctional}

\section{Performance Requirements}

\question{How much space is necessary to buffer telemetry on the spacecraft?}

\question{How much space is necessary to buffer commands on the spacecraft?}

\question{What temporal accuracy is required for time stamping telemetry?}

\question{What temporal accuracy is required for issuing commands?}

\question{Are there any latency requirements regarding the time between command issuance and command completion? This might be better documented in the command dictionary.}

\question{Are there any CPU power consumption requirements we need to know about? Sleep time?}

\section{Safety Requirements}

\question{What are our de-orbiting requirements?}

\question{What does ``safe mode'' look like? For example, if there is failure after deployment, we want to avoid damaging other spacecraft in our vicinity.}

\question{How long do we have to wait after deployment before we can do things like fire the thrusters or deploy the antenna?}

\question{In general, what is the deployment sequence? This might be more properly a functional requirement.}

\section{Security Requirements}

\question{To what extent should we be concerned about people on the ground a) monitoring the traffic to/from the spacecraft(s), and b) taking control of the spacecraft(s) by sending commands of their own? In other words: do we need to have confidentiality or data integrity in the earth to spacecraft communications link? What about the spacecraft to spacecraft link?}

\question{Do we want to require operators on the ground to authenticate to the spacecraft before they can interact with it (i.e., send commands or receive telemetry)?}

\section{Software Quality Attributes}

In what follows the phrase \newterm{code base} refers to the code that is ultimately loaded onto the spacecraft that flies in space. This document does not assert any quality rules for supporting code (that does not fly in space), although it is encouraged to follow similar rules for such code when feasible.

\begin{description}
\item[Quality.FlowErrors] The code base shall be free of flow errors in the sense meant by \SPARK. Note that without this, Quality.AORTE can't be verified by \SPARK, even in principle.

\item[Quality.AORTE] The code base shall be written in \SPARK\ and proved to be free of run time errors in the sense meant by \SPARK. Certain, limited exceptions are allowed, but they shall be documented using justifications in the source files.

\item[Quality.Functional] We rely on conventional unit and integration testing to verify functional properties of the code base. These requirements \emph{do not} require that functional properties be proved by \SPARK. However, using \SPARK\ to prove functional properties is encouraged where feasible, and may be required, to some extent, in a future version of these requirements.

\item[Quality.Testability] Library components of the code base and easily factored module sub-functionality shall be tested by unit tests that can be executed and verified automatically. Full module functionality may be tested by manual tests (due to the nature of CubedOS modules), although finding a way to verify their behavior automatically would be desirable. The manual tests do not relax the Quality.Coverage requirement (indeed, the manual tests will be needed to meet the requirement).

\item[Quality.Coverage] Test coverage shall include the execution of every line of code in the code base by some test, as documented by the output of a suitable coverage tool (such as \command{gcov}).

\item[Quality.Style] The code base shall be written according to an agreed-upon style using a style checking tool to enforce that style. The details of the style are not specified here, but are instead described in the style checking tool's configuration file.

\item[Quality.Documentation] The code base shall be documented at two levels: The public interface of every package shall be documented using a standard API documentation extraction tool such as \command{gnatdoc}. The higher level functionality of the code base shall be documented using ordinary English prose.
  
\item[Quality.CI] A continuous integration server shall be configured to perform the following steps on at least a daily basis:
  \begin{itemize}
  \item Verify clean, warning-free compilation of the code base and test programs.
  \item Verify Quality.FlowErrors
  \item Verify Quality.AORTE
  \item Verify error-free execution of the unit and integration tests (to the greatest extent possible... some tests might be difficult to automate).
  \item Verify Quality.Coverage
  \item Verify Quality.Style
  \item Extract the API documentation (see Quality.Documentation)
  \item Verify error-free compilation of the high level documentation (see Quality.Documentation)
  \end{itemize}

\item[Quality.Commit] All commits to the code base shall compile without error, all tests shall pass, and all style rules shall pass or else the commit is considered ``invalid'' and must be corrected immediately. It is understood, however, that compile-time warnings, Quality.FlowErrors, Quality.AORTE, and Quality.Coverage may be temporarily unsatisfied during the development process.

\item[Quality.Reusability] Non-hardware specific components of the code base shall be written so they could potentially be reused in other missions. Hardware specific components shall be written so they could potentially be reused in other missions using the same hardware.

\end{description}

\section{Business Rules}

% List any operating principles about the product, such as which
% individuals or roles can perform which functions under specific
% circumstances. These are not functional requirements in themselves,
% but they may imply certain functional requirements to enforce the
% rules.

\section{Other Requirements}

\question{Somewhere we need to specify what software telemetry is required. This might be better done where the telemetry dictionary is specified.}

\begin{description}
\item[Other.SourceFormat] Source files of the code base shall be Unicode files encoded with UTF-8. Latin and Greek letters are allowed in identifier names (and digits, etc., but no other letters). This is useful for writing code that directly translates mathematical equations.

\item[Other.License] \question{What license should we use for the code base?}

\item[Other.DataFormat] \question{Do we have requirements for the data format to use for telemetry data?}

\item[Other.GroundSystem] \question{To what extent are we writing ground system software? If we are it might need an separate requirements document of its own.}
\end{description}
